DATA 621---Business Analytics and Data Mining

### 2020-09-21 HW1/HW1_Group2.Rmd
Copyedit

It was interesting to compare the three models given that their performance
statistics, error measurements, and residual distributions were not drastically 
different from each other. **Model #2: Pairwise** was the worst performing model 
for all of our metrics, and was eliminated immediately. **Model #3: K-fold** accounts 
for nearly 45% of the variation in the dependent variable with the independent 
variables because its \(R^2\) is 0.456 and its adjusted \(R^2\) is = 0.450, both of 
which are acceptable for a good model. However, **Model #1: Backwards** has the 
smallest RSME of all the models. RMSE is a measure of how far off predictions are 
from the actual, giving extra weight to outliers through summing the squared
differences. This demonstrates a greater reduction in the randomness by
**Model #1: Backwards**. But its difference from **Model #3: K-fold** is only
0.022. It is hard to judge if that is a significant difference. We thus also
considered AIC. With AIC, it is not the magnitude of the value which is
important, but the difference between the various model AIC's. The magnitude is
a function of the number of observations. Accepted rules of thumb in the
statistical literature are that if the difference is greater than 10, there is
effectively no support for the model with the larger AIC
(Section 2.6, Burnham & Anderson 2002). As a result, **Model #1: Backwards**
is our selected model.

## Discussion
This is an interesting model in that given no other information, a team would be
expected to win negative games, which is clearly impossible. That being said, it
is an indication of the predictive power of the engineereed **slugging** feature
that allows small increments in slugging to result in significant shifts in
target wins. This engineered feature contains within it numerous interactions.
It combines scaled versions of some features and normalizes them for the
combination of other features. Perhaps that is why it is so significant.

@@

```{r eval_set, eval=FALSE}
# predict target wins
eval_set = eval_set %>% na.omit() %>%
  summarise(iqr = IQR(TEAM_PITCHING_SO)) %>%
  bind_cols(eval_set) %>%
  filter(TEAM_PITCHING_SO > quantile(TEAM_PITCHING_SO, probs = c(0.25), na.rm = TRUE) 
         - 1.5 * iqr, 
         TEAM_PITCHING_SO < quantile(TEAM_PITCHING_SO, probs = c(0.75), na.rm = TRUE) 
         + 1.5 * iqr) %>%
  dplyr::select(-iqr)

@@

```{r predictions}

############# predict target wins

# outlier removal - TEAM_PITCHING_SO
eval_set <- eval_set %>% na.omit() %>%
  summarise(iqr = IQR(TEAM_PITCHING_SO)) %>%
  bind_cols(eval_set) %>%
  filter(TEAM_PITCHING_SO > quantile(TEAM_PITCHING_SO, probs = c(0.25), na.rm = TRUE) 
         - 1.5 * iqr, 
         TEAM_PITCHING_SO < quantile(TEAM_PITCHING_SO, probs = c(0.75), na.rm = TRUE) 
         + 1.5 * iqr) %>%
  dplyr::select(-iqr)

>>>>

It was interesting to compare the three models given that their performance
statistics, error measurements, and residual distributions were not drastically 
different from each other. **Model #2: Pairwise** was the worst performing model 
for all of our metrics, and was eliminated immediately. **Model #3: K-fold**
accounts for nearly 45% of the variation in the dependent variable with the
independent variables because its \(R^2\) is 0.456 and its adjusted \(R^2\) is
0.450, both of which are acceptable for a good model. However,
**Model #1: Backwards** has the smallest RSME of all the models. RMSE is a
measure of how far off predictions are from the actual, giving extra weight to
outliers through summing the squared differences. This demonstrates a greater
reduction in the randomness by **Model #1: Backwards**. But its difference from
**Model #3: K-fold** is only 0.022. It is hard to judge if that is a significant
difference. We thus also considered AIC. With AIC, it is not the magnitude of
the value which is important, but the difference between the various model
AIC's. The magnitude is a function of the number of observations. Accepted rules
of thumb in the statistical literature are that if the difference is greater
than 10, there is effectively no support for the model with the larger AIC
(Section 2.6, Burnham & Anderson 2002). As a result, **Model #1: Backwards** is
our selected model.

## Discussion
This is an interesting model in that given no other information, a team would be
expected to win negative games, which is clearly impossible. That being said, it
is an indication of the predictive power of the engineered **slugging** feature
that allows small increments in slugging to result in significant shifts in
target wins. This engineered feature contains within it numerous interactions.
It combines scaled versions of some features and normalizes them for the
combination of other features. Perhaps that is why it is so significant.

@@

```{r eval_set, eval=FALSE}
# Predict target wins
eval_set = eval_set %>% na.omit() %>%
  summarise(iqr = IQR(TEAM_PITCHING_SO)) %>%
  bind_cols(eval_set) %>%
  filter(TEAM_PITCHING_SO > quantile(TEAM_PITCHING_SO, probs = c(0.25), na.rm = TRUE) 
         - 1.5 * iqr, 
         TEAM_PITCHING_SO < quantile(TEAM_PITCHING_SO, probs = c(0.75), na.rm = TRUE) 
         + 1.5 * iqr) %>%
  dplyr::select(-iqr)

@@

```{r predictions}
# Predict target wins
# outlier removal - TEAM_PITCHING_SO
eval_set <- eval_set %>% na.omit() %>%
  summarise(iqr = IQR(TEAM_PITCHING_SO)) %>%
  bind_cols(eval_set) %>%
  filter(TEAM_PITCHING_SO > quantile(TEAM_PITCHING_SO, probs = c(0.25), na.rm = TRUE) 
         - 1.5 * iqr, 
         TEAM_PITCHING_SO < quantile(TEAM_PITCHING_SO, probs = c(0.75), na.rm = TRUE) 
         + 1.5 * iqr) %>%
  dplyr::select(-iqr)
